### 2018-04-03 pubs/itp-2018/sections/proof-reconstruction.tex
[ Sec4 ] example of the strip inference.

\input{sections/diagram.tex}
The overview of the proof-reconstruction is presented as the workflow
in Fig.~\ref{fig:proof-reconstruction-workflow} following the same
basis of the proposed workflow presented in~\cite{sultana2015}.

The process begins with a \TPTP file that encodes a \CPL conjecture.
Then, we use the \Metis prover to generate a derivation of the proof
in \TSTP format in case the \CPL conjecture corresponds to a theorem.
If so, the process continues. The next step is in charge of the
\Athena translator tool that generates an \Agda file.
Athena first parses the \TSTP file, then analyzes its
derivation and generates a representation of the natural deduction
proof. In the \Athena analysis, some unnecessary steps are removed
mainly because of they introduce redundancies or they do not appear in
the proof-tree. The Agda file genereted by \Athena uses names of functions
and theorems from the \Agda libraries that accompany this article:
\texttt{agda-prop} and \texttt{agda-metis}.

Finally, we type-check the proof-terms of the \Agda file.
If this type-checking success, the \TSTP derivation generated by \Metis will be
\emph{correct} module the \Agda correctness and the completeness of the
proposed formalisation and \Agda will output an interface file.

Otherwise, when the type-checking fails, the failure must be
investigated by the user. The possible causes can be due to
a \emph{completeness} issue in our \Agda libraries for the \Metis reasoning
but also in a translation bug in \Athena. We have also consider
errors due to some failure in the type-checker~\Agda,
soundness bugs in the \Metis prover.

@@

In this section, we reconstruct each \Metis inference rule in
Table~\ref{tab:agda-metis-table}.
We begin describing the reconstruction of the \strip inference rule
since this rule  is the only one that closely follows the \Metis
source code. To reconstruct the other rules, we use a pattern for their
formalization showed in Example~\ref{ex:inference-rule-pattern}.

>>>>

\input{sections/diagram.tex}
The overview of the proof-reconstruction is presented as a workflow
in Fig.~\ref{fig:proof-reconstruction-workflow} following the same
basis of the proposed workflow presented in~\cite{sultana2015}.

The process begins with a \TPTP file that encodes a \CPL conjecture.
Then, we use the \Metis prover to generate in \TSTP format a derivation
of the proof in case the \CPL conjecture corresponds to a theorem.
If so, the process continues. The next step is in charge of the
\Athena translator tool that generates an \Agda file.
Athena first parses the \TSTP file, then analyzes its
derivation and generates a representation of the natural deduction
proof. In the analysis, some unnecessary steps read from the \TSTP derivation
are taken into account in the final proof-tree mainly because some introduce redundancies
or they do not contribute in the proof.
The Agda file genereted by \Athena uses names of functions
and theorems from the \Agda libraries that accompany this article:
\texttt{agda-prop} and \texttt{agda-metis}.

Using \Agda as the proof-checker, we type-check the proof-terms of the
\Agda file previous generated. If this type-checking success, the
\TSTP derivation generated by \Metis will be \emph{correct} module the
\Agda correctness and the proposed formalisation.
In such a case, \Agda will output an interface file. Otherwise, when
the type-checking fails, the failure must be investigated by the user.
The possible causes can be due to many factors: a
\emph{completeness} issue in our \Agda libraries for the \Metis
reasoning, a translation bug in \Athena, errors in \Agda, printing or
soundness bugs in the \Metis prover.

@@

In this section, we reconstruct each \Metis inference rule from
Table~\ref{tab:agda-metis-table}.
We begin describing the reconstruction of the \strip inference rule
since this rule  is the only one that closely follows the \Metis
source code. To reconstruct the other rules, we follow a pattern showed
in Example~\ref{ex:inference-rule-pattern}.

### 2018-04-03 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ Sec4 ] example of the strip inference.

\begin{myexamplenum}

The subgoals associated to a goal are introduced
in the \TSTP derivation with the \strip inference rule.

\begin{verbatim}
  fof(goal, conjecture, (p ∧ r) ∧ q)).
  fof(s₁, p, inf(strip, goal)).
  fof(s₂, p ⇒ r, inf(strip, goal)).
  fof(s₃, (p ∧ r) ⇒ q, inf(strip, goal)).
\end{verbatim}

In this example, the conjecture $(p ∧ r) ∧ q$ is stripped into
tree subgoals: $p$, $p ⇒ r$ and $(p ∧ r) ⇒ q$.

\begin{equation}
\label{eq:strip-example}
(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q).
\end{equation}

\Metis proves each subgoal in the same order above from left to right
in~\eqref{eq:strip-example}.
So far, very little attention has been paid to the role of the \strip rule
in \TSTP derivations since \Metis does not make explicit the way
it uses the subgoals to prove the conjecture.
\end{myexamplenum}

We prove the correctness of the \strip inference rule in
Theorem~\ref{thm:strip}. To show that theorem, we need to prove
Lemma~\ref{lem:inv-uh-lem} and Lemma~\ref{lem:lem-inv-strip}.

>>>>

\begin{myexamplenum}
In Fig.~\ref{complete-metis-example}, we can see how
the subgoals associated to a goal are introduced
in the \TSTP derivation line \ref{line3} with the \strip inference rule.
The conjecture in line \ref{line2}, $(p ∨ q) ⇒ (p ∧ q)$,
is stripped into two subgoals (line~\ref{line4} and \ref{line5}):
$(p ∨ q) ⇒ p$ and $((p ∨ q) ∧ p) ⇒ q$.
\Metis proves each subgoal separately following the same order as
they appeared in the \TSTP derivation.
\end{myexamplenum}

Unluckily, \Metis does not make explicit the way it uses the subgoals
to prove the goal by the time this document is written. Thus we show the
explicit description of this stripping process in the correctness of
the \strip inference rule in Theorem~\ref{thm:strip}. We first need
to prove Lemma~\ref{lem:inv-uh-lem} and Lemma~\ref{lem:lem-inv-strip}.
